Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-09 STAT-paper-template/APA/response-to-reviewers.md

There is not currently a functionality for this, but it is definitely something of interest for the future. As a result, we have added it to the future work section!

**Additional Changes**

The first two bullets in the future work section have been completed since the submission of the original manuscript. Due to this, those bullets have been removed and replaced with new future steps.

Additionally, a new bullet point on code commenting (relevant to the has_well_commented_code() function as well as one of the added sources), has been added to the summary of reproducibility components.

### 2020-10-09 STAT-paper-template/APA/fertile.Rnw
updating w/ fertile

<<fertile, message = FALSE, warning = FALSE, error = TRUE>>=
library(fertile)
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
read.csv("../../../Desktop/my_data.csv")
@

\textcolor{blue}{Users who want to override this behavior and execute their function anyway are provided with a explanation of how to do so.}

>>>>

<<fertile, message = FALSE, warning = FALSE, error = TRUE>>=
library(fertile)
library(readr)
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
read_csv("../../../Desktop/my_data.csv")
@

\textcolor{blue}{Users who want to override this behavior and execute their function anyway are provided with a piece of code to execute that will achieve this for them.}

### 2020-10-09 STAT-paper-template/APA/fertile.tex
updating w/ fertile

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(fertile)}
\hlkwd{file.exists}\hlstd{(}\hlstr{"~/Desktop/my_data.csv"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\begin{alltt}
\hlkwd{read.csv}\hlstd{(}\hlstr{"~/Desktop/my_data.csv"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected absolute paths. Absolute paths are not reproducible and will likely only work on your computer. If you would like to continue anyway, re-execute your command by typing the name of the package it originates from followed by :: and the function call, e.g. if you previously typed 'read\_csv(path)', instead use 'readr::read\_csv(path)'}}\begin{alltt}
\hlkwd{read.csv}\hlstd{(}\hlstr{"../../../Desktop/my_data.csv"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected paths that lead outside the project directory. Such paths are not reproducible and will likely only work on your computer. If you would like to continue anyway, re-execute your command by typing the name of the package it originates from followed by :: and the function call, e.g. if you previously typed 'read\_csv(path)', instead use 'readr::read\_csv(path)'}}\end{kframe}
\end{knitrout}

\textcolor{blue}{Users who want to override this behavior and execute their function anyway are provided with a explanation of how to do so.}

@@

\includegraphics[width=500pt,height=280pt]{list-checks}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... ----------------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks ----------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for no absolute paths}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for only portable paths}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks ---------------------------------------------- fertile 0.0.0.9027 --}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Reproducibility checks passed: 2}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps ------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code ----------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory ------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 4
##   file               ext        size mime                                       
##   <fs::path>         <chr> <fs::byt> <chr>                                      
## 1 Estrogen_Receptor~ docx     10.97K application/vnd.openxmlformats-officedocum~
## 2 citrate_v_time.png png     184.04K image/png                                  
## 3 proteins_v_time.p~ png     377.02K image/png                                  
## 4 Blot_data_updated~ csv      14.43K text/csv                                   
## 5 CS_data_redone.csv csv       7.39K text/csv                                   
## 6 mice.csv           csv      14.33K text/csv                                   
## 7 README.md          md           39 text/markdown                              
## 8 miceps.Rproj       Rproj       204 text/rstudio                               
## 9 analysis.Rmd       Rmd       4.94K text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files ----------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 7 x 3
##   path_rel           dir_rel    cmd                                             
##   <fs::path>         <fs::path> <chr>                                           
## 1 Blot_data_updated~ data-raw   file_move('project_miceps/Blot_data_updated.csv~
## 2 CS_data_redone.csv data-raw   file_move('project_miceps/CS_data_redone.csv', ~
## 3 Estrogen_Receptor~ inst/other file_move('project_miceps/Estrogen_Receptors.do~
## 4 analysis.Rmd       vignettes  file_move('project_miceps/analysis.Rmd', fs::di~
## 5 citrate_v_time.png inst/image file_move('project_miceps/citrate_v_time.png', ~
## 6 mice.csv           data-raw   file_move('project_miceps/mice.csv', fs::dir_cr~
## 7 proteins_v_time.p~ inst/image file_move('project_miceps/proteins_v_time.png',~
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged --------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-09 15:45:45
## 2 package:for~ <NA>                                 base::l~ 2020-10-09 15:45:45
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-09 15:45:45
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file)
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7fb02d55d1b0>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected absolute paths. Absolute paths are not reproducible and will likely only work on your computer. If you would like to continue anyway, re-execute your command by typing the name of the package it originates from followed by :: and the function call, e.g. if you previously typed 'read\_csv(path)', instead use 'readr::read\_csv(path)'}}\begin{alltt}
\hlcom{# Path outside the directory}
\hlkwd{check_path}\hlstd{(}\hlstr{"../fertile.Rmd"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected paths that lead outside the project directory. Such paths are not reproducible and will likely only work on your computer. If you would like to continue anyway, re-execute your command by typing the name of the package it originates from followed by :: and the function call, e.g. if you previously typed 'read\_csv(path)', instead use 'readr::read\_csv(path)'}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpOuHj47/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpOuHj47/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpOuHj47/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpOuHj47/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(fertile)}
\hlkwd{library}\hlstd{(readr)}
\hlkwd{file.exists}\hlstd{(}\hlstr{"~/Desktop/my_data.csv"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\begin{alltt}
\hlkwd{read.csv}\hlstd{(}\hlstr{"~/Desktop/my_data.csv"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected absolute paths. Absolute paths are not reproducible and will likely only work on your computer. If you would like to continue anyway, please execute the following command: utils::read.csv('\textasciitilde{}/Desktop/my\_data.csv')}}\begin{alltt}
\hlkwd{read_csv}\hlstd{(}\hlstr{"../../../Desktop/my_data.csv"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected paths that lead outside the project directory. Such paths are not reproducible and will likely only work on your computer. If you would like to continue anyway, please execute the following command: readr::read\_csv('../../../Desktop/my\_data.csv')}}\end{kframe}
\end{knitrout}

\textcolor{blue}{Users who want to override this behavior and execute their function anyway are provided with a piece of code to execute that will achieve this for them.}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}

\caption{\label{tab:list-of-checks}Table illustrating the list of check available in fertile. }
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright\arraybackslash}p{4in}}
\toprule
Check & Functionality\\
\midrule
\cellcolor{gray!6}{has\_proj\_root()} & \cellcolor{gray!6}{Checks to make sure a single .Rproj file is found in the root directory of the project.}\\
has\_no\_nested\_proj\_root() & Checks to make sure there are no nested .Rproj files in subfolders of the project.\\
\cellcolor{gray!6}{has\_clear\_build\_chain()} & \cellcolor{gray!6}{Looks for indication of a clear order in which to run R scripts.}\\
has\_tidy\_[media/images/code/raw\_data/data/scripts]() & There are six different 'has\_tidy\_...' functions. Each checks to make sure that no files of its given type (images, code, data, etc.) are located in the root directory of the project\\
\cellcolor{gray!6}{has\_only\_used\_files()} & \cellcolor{gray!6}{Ensures that all files located in the project directory are being referenced or created by other files in the project.}\\
\addlinespace
has\_readme() & Checks to make sure there is a README file in the root directory.\\
\cellcolor{gray!6}{has\_well\_commented\_code()} & \cellcolor{gray!6}{Checks to ensure that all code files contain an adequate number of comments (>10\% of lines).}\\
has\_no\_absolute\_paths() & Checks to make sure that no absolute paths are referenced in code.\\
\cellcolor{gray!6}{has\_only\_portable\_paths()} & \cellcolor{gray!6}{Checks to make sure that no paths in code lead outside the project directory.}\\
has\_no\_randomness() & Checks to make sure code does not contain uncontrolled randomness.\\
\addlinespace
\cellcolor{gray!6}{has\_no\_lint()} & \cellcolor{gray!6}{Examines code to determine whether it conforms to 'tidy' style guide recommendations.}\\
\bottomrule
\end{tabu}
\end{table}

\end{knitrout}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... --------------------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ----------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Error in eval\_tidy(xs[[j]], mask): object '.Random.seed' not found}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks --------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: arrange() failed at implicit mutate() step. \\\#\# x Could not create a temporary column for `..1`.\\\#\# i `..1` is `timestamp`.}}\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: arrange() failed at implicit mutate() step. \\\#\# x Could not create a temporary column for `..1`.\\\#\# i `..1` is `timestamp`.}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-09 23:56:28
## 2 package:for~ <NA>                                 base::l~ 2020-10-09 23:56:28
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-09 23:56:28
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file, ... = "readr::read_csv")
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7fe67a348478>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected absolute paths. Absolute paths are not reproducible and will likely only work on your computer.}}\begin{alltt}
\hlcom{# Path outside the directory}
\hlkwd{check_path}\hlstd{(}\hlstr{"../fertile.Rmd"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected paths that lead outside the project directory. Such paths are not reproducible and will likely only work on your computer.}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpisOoIV/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpisOoIV/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpisOoIV/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpisOoIV/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}
